Global case

### 2025-05-06 lipschitz/Lipitschz.tex
update

	Recall the definition of Lipschitz continuity:
	 under distance $d$, a function $f(x)$ is Lipschitz continuous with respect to constant $K$ if:
	\begin{align*}
		\forall \boldsymbol{x} \forall\boldsymbol{y} (|f(\boldsymbol{x}) -f(\boldsymbol{y}) |\leq K|\boldsymbol{x}-\boldsymbol{y}|)
	\end{align*}

	In our practice of global robustness, we will consider the following weaker property with respect to a certain number $\epsilon$:

	\begin{align*}
		\forall \boldsymbol{x} \forall\boldsymbol{y} &  (|\boldsymbol{x}-\boldsymbol{y}| \geq \epsilon \implies|f(\boldsymbol{x}) -f(\boldsymbol{y}) |\leq K|\boldsymbol{x}-\boldsymbol{y}|\\
		&  |\boldsymbol{x}-\boldsymbol{y}| < \epsilon \implies|f(\boldsymbol{x}) -f(\boldsymbol{y}) |\leq K\epsilon)
	\end{align*}

>>>>

	Recall the definition of Lipschitz continuity:
	 under distance $d$, a function $f(x)$ is Lipschitz continuous with respect to constant $K$ if:
	\begin{align*}
		\forall \boldsymbol{x} \forall\boldsymbol{y} (|f(\boldsymbol{x}) -f(\boldsymbol{y}) |\leq K|\boldsymbol{x}-\boldsymbol{y}|)
	\end{align*} 
	In our practice of global robustness, we will consider the following weaker property with respect to a certain number $\epsilon$:
	\begin{align*}
		\forall \boldsymbol{x} \forall\boldsymbol{y} &  (|\boldsymbol{x}-\boldsymbol{y}| \geq \epsilon \implies|f(\boldsymbol{x}) -f(\boldsymbol{y}) |\leq K|\boldsymbol{x}-\boldsymbol{y}|\\
		&  |\boldsymbol{x}-\boldsymbol{y}| < \epsilon \implies|f(\boldsymbol{x}) -f(\boldsymbol{y}) |\leq K\epsilon)
	\end{align*} 
	In terms of the code, it is compute an optimization question respect to a certain number $\epsilon$:	\begin{align*}
			\max_{|\boldsymbol{x}-\boldsymbol{y}| \leq \epsilon} |f(\boldsymbol{x}) -f(\boldsymbol{y}) |
	\end{align*} We can use this maximum value to estimate the Lipschitz constant.
